---
title: "Data Exploration and Analytical Decisions"
author: "Luke J. Eberhart-Phillips and Martin Bulla"
date: "8/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Import

```{r data import}
BT_data <- read.csv("../Data/blue_tit_data.csv")
```

## Libraries

```{r, message = FALSE}
library(tidyverse)
library(lme4)
library(standardize)
library(kableExtra)
```

## Plotting Theme
```{r}
# define the plotting theme to be used in subsequent ggplots
luke_theme <- 
  theme_bw() +
  theme(
    text = element_text(family = "Franklin Gothic Book"),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    axis.title.x = element_text(size = 10),
    axis.text.x  = element_text(size = 8), 
    axis.title.y = element_text(size = 10),
    axis.text.y = element_text(size = 8),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.5, colour = "grey40"),
    axis.ticks.length = unit(0.2, "cm"),
    panel.border = element_rect(linetype = "solid", colour = "grey")
  )

# set the ggplotting theme
theme_set(luke_theme)
```

## Distributions of variables of interest

Step one:
- distribution of hatching dates and brood sizes between treatment categories to see whether the design was balanced and thus controlling for environmental and social factors (like differences in hatch date) are not necessary; if well matched across treatments (90%) we will attempt analyses with nest pairs (reduced/increased) or triads (reduced/increase/unmanipulated), i.e. no need to control for differences between reared and hatched nest; if the match is <90% we will control the models for the age differences between the reared and hatch nests

### Brood Sizes

```{r brood size distribution plots}
# plot of d0_hatch_nest_brood_size based on treatment
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size)),
         
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>% 
  # histogram of brood size distribution across the three levels of treatment
  ggplot() +
  geom_histogram(aes(d0_hatch_nest_brood_size), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  facet_grid(. ~ rear_nest_trt)

# plot of rear_d0_rear_nest_brood_size based on treatment
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size)),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>% 
  # histogram of brood size distribution across the three levels of treatment
  ggplot() +
  geom_histogram(aes(rear_d0_rear_nest_brood_size), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  facet_grid(. ~ rear_nest_trt)

# plot of rear_Cs_at_start_of_rearing based on treatment
BT_data %>% 
  # change "." to "NA"
  mutate(rear_Cs_at_start_of_rearing = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(rear_Cs_at_start_of_rearing = as.numeric(as.character(rear_Cs_at_start_of_rearing)),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>% 
  # histogram of brood size distribution across the three levels of treatment
  ggplot() +
  geom_histogram(aes(rear_Cs_at_start_of_rearing), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  facet_grid(. ~ rear_nest_trt)
```

```{r}
# plot of rear_Cs_at_start_of_rearing based on treatment
BT_data %>% 
  # change "." to "NA"
  mutate(rear_Cs_at_start_of_rearing = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(rear_Cs_at_start_of_rearing = as.numeric(as.character(rear_Cs_at_start_of_rearing)),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>% 
  # histogram of brood size distribution across the three levels of treatment
  ggplot() +
  geom_histogram(aes(rear_Cs_at_start_of_rearing), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  facet_grid(. ~ rear_nest_trt)
```


*Increase*
```{r brood size distribution table increase}
# proportional table of d0_hatch_nest_brood_size based on treatment
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size)),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>% 
  count(rear_nest_trt, d0_hatch_nest_brood_size) %>% 
  group_by(rear_nest_trt) %>% 
  mutate(prop = prop.table(n)) %>% 
  filter(rear_nest_trt == "increase") %>% 
  collect() %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "80%")
```

*Decrease*
```{r brood size distribution table decrease}
# proportional table of d0_hatch_nest_brood_size based on treatment
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size)),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>% 
  count(rear_nest_trt, d0_hatch_nest_brood_size) %>% 
  group_by(rear_nest_trt) %>% 
  mutate(prop = prop.table(n)) %>% 
  filter(rear_nest_trt == "decrease") %>% 
  collect() %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "80%")
```

*Control*
```{r brood size distribution table control}
# proportional table of d0_hatch_nest_brood_size based on treatment
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size)),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>% 
  count(rear_nest_trt, d0_hatch_nest_brood_size) %>% 
  group_by(rear_nest_trt) %>% 
  mutate(prop = prop.table(n)) %>% 
  filter(rear_nest_trt == "control") %>% 
  collect() %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "80%")
```
Following this, it seems like 8 might be a good cutoff for the two groups of brood size (i.e., d0_hatch_nest_brood_size < 8 then "small", d0_hatch_nest_brood_size > 8 then "large")

Need to check how well nests were paired according to brood size (e.g., Nest 1 had 12 chicks and Nest 2 also had 12 chicks)
```{r brood size differences in pairs}
# plot of the difference in brood size between paired nests
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size))) %>% 
  
  # calculate differences in brood size between hatch and rear nests
  mutate(diff_brood_size = d0_hatch_nest_brood_size - rear_d0_rear_nest_brood_size,
         
         # create a group variable specifying if it was a small or large nest
         brood_size_group = ifelse(d0_hatch_nest_brood_size > 8, "large", "small"),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>%
  filter(!is.na(brood_size_group)) %>% 
  ggplot() +
  geom_histogram(aes(diff_brood_size), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  xlab("Difference in brood size between paired nests") +
  facet_grid(rear_nest_trt ~ brood_size_group)
```

```{r prop table for large nest pairs}
# proportional table of differences in brood sizes for nests > 8 
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size))) %>% 
  
  # calculate differences in brood size between hatch and rear nests
  mutate(diff_brood_size = d0_hatch_nest_brood_size - rear_d0_rear_nest_brood_size,
         
         # create a group variable specifying if it was a small or large nest
         brood_size_group = ifelse(d0_hatch_nest_brood_size > 8, "large", "small"),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>%
  filter(!is.na(brood_size_group)) %>% 
  count(brood_size_group, diff_brood_size) %>% 
  group_by(brood_size_group) %>% 
  mutate(prop = prop.table(n)) %>% 
  filter(brood_size_group == "large") %>% 
  collect() %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "80%")
```

```{r prop table for small nest pairs}
# proportional table of differences in brood sizes for nests < 8 
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size))) %>% 
  
  # calculate differences in brood size between hatch and rear nests
  mutate(diff_brood_size = d0_hatch_nest_brood_size - rear_d0_rear_nest_brood_size,
         
         # create a group variable specifying if it was a small or large nest
         brood_size_group = ifelse(d0_hatch_nest_brood_size > 8, "large", "small"),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>%
  filter(!is.na(brood_size_group)) %>% 
  count(brood_size_group, diff_brood_size) %>% 
  group_by(brood_size_group) %>% 
  mutate(prop = prop.table(n)) %>% 
  filter(brood_size_group == "small") %>% 
  collect() %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "80%")
```

identify the "weird" outlier pairs that have much different brood sizes. need to think about what to do with these pairs.
```{r weird pairs}
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size))) %>% 
  
  # calculate differences in brood size between hatch and rear nests
  mutate(diff_brood_size = d0_hatch_nest_brood_size - rear_d0_rear_nest_brood_size,
         
         # create a group variable specifying if it was a small or large nest
         brood_size_group = ifelse(d0_hatch_nest_brood_size > 8, "large", "small"),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>%
  filter(!is.na(brood_size_group)) %>% 
  filter(diff_brood_size < -6 | diff_brood_size > 9) %>% 
  select(hatch_nest_breed_ID, rear_nest_breed_ID, d0_hatch_nest_brood_size, rear_d0_rear_nest_brood_size, diff_brood_size, rear_nest_trt, brood_size_group) %>%
  distinct() %>% 
  arrange(hatch_nest_breed_ID)
```

### Hatch Dates
First need to check the time difference (in days) between the hatch date of the hatch nest and the hatch date of the rear nest. Ideally, these two are perfectly matched (as described in the methods) and have a difference of 0 days.
```{r hatch dates check}
# 25 cases in which the rear_nest had a hatch date 1 day after the hatch_nest (0.7%)
# 13 cases in which the rear_nest had a hatch date 1 day before the hatch_nest (0.4%)
# 3682 cases in which the hatch date of the rear_nest matched that of the hatch_nest (98.7%)
BT_data %>% 
  summarise(date_matching = hatch_nest_OH - rear_nest_OH) %>% 
  ggplot() +
  geom_histogram(aes(date_matching), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity")
BT_data %>% 
  summarise(date_matching = hatch_nest_OH - rear_nest_OH) %>% 
  mutate_all(as.factor) %>%
  select(date_matching) %>% 
  summary()

# seems like the matching was very successful! We can likely simply use the rear_nest hatch date then
```

Check annual variation in nesting phenology
```{r hatch date standardization}
# plot seasonal hatch date variation by year
BT_data %>% 
  ggplot() +
  geom_histogram(aes(rear_nest_OH), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  facet_grid(hatch_year ~ .)

# wow, big differences! need to standardize hatch date by year to make years comparable

# standardize the hatch date of the rear_nest by year
BT_data <- 
  BT_data %>% 
  mutate(rear_nest_OH_std = as.numeric(scale_by(rear_nest_OH ~ hatch_year, .)))

# plot standardized hatch date variation by year
BT_data %>% 
  ggplot() +
  geom_histogram(aes(rear_nest_OH_std), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  facet_grid(hatch_year ~ .)

# great this looks good now
```

Assesment of matching by brood size and hatch date:
- the vast majority of pairs have the brood sizes that are within 1 chick difference (>80%)
- there is a strange subset of nests that had extreme differences in brood size (likley due to availability of nests at a given time point in the season. I would guess that matching the age of chicks (i.e., hatch date) was prioritized over brood size)
- Almost all pairs are matched for hatch date (99%) so this is not an issue to control for
- to proceed with the pair-based analysis, perhaps we should limit it to nests that are within 5 chicks of each other (based on the distribution shown in the following plot)

```{r hatch dates vs brood size difference plot}
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size))) %>% 
  
  # calculate differences in brood size between hatch and rear nests
  mutate(diff_brood_size = d0_hatch_nest_brood_size - rear_d0_rear_nest_brood_size,
         
         # create a group variable specifying if it was a small or large nest
         brood_size_group = ifelse(d0_hatch_nest_brood_size > 8, "large", "small"),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>%
  filter(!is.na(brood_size_group)) %>% 
  ggplot() +
  geom_point(aes(y = diff_brood_size, x = rear_nest_OH_std), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  geom_hline(yintercept = 5, linetype = "dashed", color = "lightgrey") +
  geom_hline(yintercept = -5, linetype = "dashed", color = "lightgrey") +
  ylab("Difference in brood size between paired nests") +
  xlab("Standardized hatch date of rear nest") +
  facet_grid(rear_nest_trt ~ brood_size_group)
```