---
title: "Data Exploration and Analytical Decisions"
author: "Luke J. Eberhart-Phillips and Martin Bulla"
date: "8/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```

## Data Import

```{r data import}
BT_data <- read.csv("../Data/blue_tit_data.csv")
```

## Libraries

```{r, message = FALSE}
library(tidyverse)
library(lme4)
library(standardize)
library(kableExtra)
```

## Plotting Theme
```{r}
# define the plotting theme to be used in subsequent ggplots
luke_theme <- 
  theme_bw() +
  theme(
    text = element_text(family = "Franklin Gothic Book"),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    axis.title.x = element_text(size = 10),
    axis.text.x  = element_text(size = 8), 
    axis.title.y = element_text(size = 10),
    axis.text.y = element_text(size = 8),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_line(size = 0.5, colour = "grey40"),
    axis.ticks.length = unit(0.2, "cm"),
    panel.border = element_rect(linetype = "solid", colour = "grey")
  )

# set the ggplotting theme
theme_set(luke_theme)
```

## Distributions of variables of interest

Step one:
check the distribution of hatching dates and brood sizes between treatment categories to see whether the design was balanced. 

If not balanced we will need to control for environmental and social factors (like differences in hatch date and brood size); if well matched across treatments (90%) we will attempt analyses with nest pairs (reduced/increased) or triads (reduced/increase/unmanipulated), i.e. no need to control for differences between reared and hatched nest; if the match is <90% we will control the models for the age differences between the reared and hatch nests and brood size. 

### Brood Sizes

#### What is a good cutoff for the "small" and "large" broods?
plot of d0_hatch_nest_brood_size based on treatment
```{r brood size distribution plots}
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size)),
         
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>% 
  # histogram of brood size distribution across the three levels of treatment
  ggplot() +
  geom_histogram(aes(d0_hatch_nest_brood_size), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  facet_grid(. ~ rear_nest_trt)
```
plot of rear_d0_rear_nest_brood_size based on treatment
```{r}
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size)),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>% 
  # histogram of brood size distribution across the three levels of treatment
  ggplot() +
  geom_histogram(aes(rear_d0_rear_nest_brood_size), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  facet_grid(. ~ rear_nest_trt)
```
plot of rear_Cs_at_start_of_rearing based on treatment
```{r}
BT_data %>% 
  # change "." to "NA"
  mutate(rear_Cs_at_start_of_rearing = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(rear_Cs_at_start_of_rearing = as.numeric(as.character(rear_Cs_at_start_of_rearing)),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>% 
  # histogram of brood size distribution across the three levels of treatment
  ggplot() +
  geom_histogram(aes(rear_Cs_at_start_of_rearing), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  facet_grid(. ~ rear_nest_trt)
```

proportional table of d0_hatch_nest_brood_size based on treatment *Increase*
```{r brood size distribution table increase}
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size)),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>% 
  count(rear_nest_trt, d0_hatch_nest_brood_size) %>% 
  group_by(rear_nest_trt) %>% 
  mutate(prop = prop.table(n)) %>% 
  filter(rear_nest_trt == "increase") %>% 
  collect() %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "80%")
```

proportional table of d0_hatch_nest_brood_size based on treatment *Decrease*
```{r brood size distribution table decrease}
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size)),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>% 
  count(rear_nest_trt, d0_hatch_nest_brood_size) %>% 
  group_by(rear_nest_trt) %>% 
  mutate(prop = prop.table(n)) %>% 
  filter(rear_nest_trt == "decrease") %>% 
  collect() %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "80%")
```

proportional table of d0_hatch_nest_brood_size based on treatment *Control*
```{r brood size distribution table control}
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size)),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>% 
  count(rear_nest_trt, d0_hatch_nest_brood_size) %>% 
  group_by(rear_nest_trt) %>% 
  mutate(prop = prop.table(n)) %>% 
  filter(rear_nest_trt == "control") %>% 
  collect() %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "80%")
```
Following this, it seems like 8 might be a good cutoff for the two groups of brood size (i.e., d0_hatch_nest_brood_size < 8 then "small", d0_hatch_nest_brood_size > 8 then "large")

#### Is it true that manipulations were approximately "one-fourth" of the original brood size?
NO! it seems like the manipulations were not all "one fourth" (as written in the field methods)! vertical dashed lines in this plot show 0.25% of the hatched nest brood size. Note that "large" is nests > 8 and "small" is nests < 8 chicks. It seems that most small nests experienced manipulations in brood size way more than 25%!! In other words, the bottom-middle panel shows that all the data are left of the dashed line!
```{r}
# plot of proportion of brood moved based on treatment
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         net_rearing_manipulation = ifelse(net_rearing_manipulation == ".", "NA", net_rearing_manipulation)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         net_rearing_manipulation = as.numeric(as.character(net_rearing_manipulation)),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>% 
  # create a group variable specifying if it was a small or large nest
  mutate(brood_size_group = ifelse(d0_hatch_nest_brood_size > 8, "large", "small"),
         proportional_change_in_brood_size = abs(net_rearing_manipulation) / d0_hatch_nest_brood_size) %>% 
  filter(!is.na(brood_size_group)) %>% 
  ggplot() +
  geom_histogram(aes(proportional_change_in_brood_size), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 0.1, position = "identity") +
  geom_vline(xintercept = 0.25, linetype = "dashed") +
  facet_grid(brood_size_group ~ rear_nest_trt) +
  xlab("Proportional change in brood size following manipulation")
```

#### How well are paired nests paired according to brood size?
plot of the difference in brood size between paired nests
```{r brood size differences in pairs}
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size))) %>% 
  
  # calculate differences in brood size between hatch and rear nests
  mutate(diff_brood_size = d0_hatch_nest_brood_size - rear_d0_rear_nest_brood_size,
         
         # create a group variable specifying if it was a small or large nest
         brood_size_group = ifelse(d0_hatch_nest_brood_size > 8, "large", "small"),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>%
  filter(!is.na(brood_size_group)) %>% 
  ggplot() +
  geom_histogram(aes(diff_brood_size), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  xlab("Difference in brood size between paired nests") +
  facet_grid(rear_nest_trt ~ brood_size_group)
```

proportional table of differences in brood sizes for nests > 8
```{r prop table for large nest pairs}
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size))) %>% 
  
  # calculate differences in brood size between hatch and rear nests
  mutate(diff_brood_size = d0_hatch_nest_brood_size - rear_d0_rear_nest_brood_size,
         
         # create a group variable specifying if it was a small or large nest
         brood_size_group = ifelse(d0_hatch_nest_brood_size > 8, "large", "small"),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>%
  filter(!is.na(brood_size_group)) %>% 
  count(brood_size_group, diff_brood_size) %>% 
  group_by(brood_size_group) %>% 
  mutate(prop = prop.table(n)) %>% 
  filter(brood_size_group == "large") %>% 
  collect() %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "80%")
```

proportional table of differences in brood sizes for nests < 8 
```{r prop table for small nest pairs}
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size))) %>% 
  
  # calculate differences in brood size between hatch and rear nests
  mutate(diff_brood_size = d0_hatch_nest_brood_size - rear_d0_rear_nest_brood_size,
         
         # create a group variable specifying if it was a small or large nest
         brood_size_group = ifelse(d0_hatch_nest_brood_size > 8, "large", "small"),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>%
  filter(!is.na(brood_size_group)) %>% 
  count(brood_size_group, diff_brood_size) %>% 
  group_by(brood_size_group) %>% 
  mutate(prop = prop.table(n)) %>% 
  filter(brood_size_group == "small") %>% 
  collect() %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "80%")
```

#### What are these weird outliers which have been paired even though they have extremely different initial brood sizes?
need to think about what to do with these pairs.
```{r weird pairs}
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size))) %>% 
  
  # calculate differences in brood size between hatch and rear nests
  mutate(diff_brood_size = d0_hatch_nest_brood_size - rear_d0_rear_nest_brood_size,
         
         # create a group variable specifying if it was a small or large nest
         brood_size_group = ifelse(d0_hatch_nest_brood_size > 8, "large", "small"),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>%
  filter(!is.na(brood_size_group)) %>% 
  filter(diff_brood_size < -6 | diff_brood_size > 9) %>% 
  select(hatch_nest_breed_ID, rear_nest_breed_ID, d0_hatch_nest_brood_size, rear_d0_rear_nest_brood_size, diff_brood_size, rear_nest_trt, brood_size_group) %>%
  distinct() %>% 
  arrange(hatch_nest_breed_ID) %>% 
  collect() %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "10%")
```

### Hatch Dates
First need to check the time difference (in days) between the hatch date of the hatch nest and the hatch date of the rear nest. Ideally, these two are perfectly matched (as described in the methods) and have a difference of 0 days.
```{r hatch dates check}
# 25 cases in which the rear_nest had a hatch date 1 day after the hatch_nest (0.7%)
# 13 cases in which the rear_nest had a hatch date 1 day before the hatch_nest (0.4%)
# 3682 cases in which the hatch date of the rear_nest matched that of the hatch_nest (98.7%)
BT_data %>% 
  summarise(date_matching = hatch_nest_OH - rear_nest_OH) %>% 
  ggplot() +
  geom_histogram(aes(date_matching), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity")
BT_data %>% 
  summarise(date_matching = hatch_nest_OH - rear_nest_OH) %>% 
  mutate_all(as.factor) %>%
  select(date_matching) %>% 
  summary()

# seems like the matching was very successful! We can likely simply use the rear_nest hatch date then
```

Check annual variation in nesting phenology
```{r hatch date standardization}
# plot seasonal hatch date variation by year
BT_data %>% 
  ggplot() +
  geom_histogram(aes(rear_nest_OH), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  facet_grid(hatch_year ~ .)

# wow, big differences! need to standardize hatch date by year to make years comparable

# standardize the hatch date of the rear_nest by year (correcting for the minimum hatch date)
BT_data <-
  BT_data %>% 
  group_by(hatch_year) %>% 
  summarise(min_rear_nest_OH = min(rear_nest_OH, na.rm = TRUE)) %>% 
  left_join(., BT_data, by = "hatch_year") %>% 
  mutate(rear_nest_OH_std = rear_nest_OH - min_rear_nest_OH)

# plot standardized hatch date variation by year
BT_data %>% 
  ggplot() +
  geom_histogram(aes(rear_nest_OH_std), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  facet_grid(hatch_year ~ .) 

# great this looks good now
```

### Overall assesment of matching by brood size and hatch date:
- the vast majority of pairs have the brood sizes that are within 1 chick difference (>80%)
- there is a strange subset of nests that had extreme differences in brood size (likley due to availability of nests at a given time point in the season. I would guess that matching the age of chicks (i.e., hatch date) was prioritized over brood size)
- Almost all pairs are matched for hatch date (99%) so this is not an issue to control for
- to proceed with the pair-based analysis, perhaps we should limit it to nests that are within 5 chicks of each other (based on the distribution shown in the following plot)
- Need to consider the manipulation of small nests (i.e., those with less than 8 chicks): the experiment often increased or decreased the brood size >>25%! Perhaps we should still split the analysis into small vs. large since the experiemental treatment is not comparable.
```{r hatch dates vs brood size difference plot}
BT_data %>% 
  # change "." to "NA"
  mutate(d0_hatch_nest_brood_size = ifelse(d0_hatch_nest_brood_size == ".", "NA", d0_hatch_nest_brood_size),
         rear_d0_rear_nest_brood_size = ifelse(rear_d0_rear_nest_brood_size == ".", "NA", rear_d0_rear_nest_brood_size)) %>% 
  # specify as numeric
  mutate(d0_hatch_nest_brood_size = as.numeric(as.character(d0_hatch_nest_brood_size)),
         rear_d0_rear_nest_brood_size = as.numeric(as.character(rear_d0_rear_nest_brood_size))) %>% 
  
  # calculate differences in brood size between hatch and rear nests
  mutate(diff_brood_size = d0_hatch_nest_brood_size - rear_d0_rear_nest_brood_size,
         
         # create a group variable specifying if it was a small or large nest
         brood_size_group = ifelse(d0_hatch_nest_brood_size > 8, "large", "small"),
         # re-name the treatment groups
         rear_nest_trt = ifelse(rear_nest_trt == 5, "increase", 
                                ifelse(rear_nest_trt == 6, "decrease", "control"))) %>%
  filter(!is.na(brood_size_group)) %>% 
  ggplot() +
  geom_point(aes(y = diff_brood_size, x = rear_nest_OH_std), alpha = 0.3, color = "grey40", fill = "#7570B3", 
                 binwidth = 1, position = "identity") +
  geom_hline(yintercept = 5, linetype = "dashed", color = "lightgrey") +
  geom_hline(yintercept = -5, linetype = "dashed", color = "lightgrey") +
  ylab("Difference in brood size between paired nests") +
  xlab("Standardized hatch date of rear nest") +
  facet_grid(rear_nest_trt ~ brood_size_group)
```